---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a) Video Summary

For this assignment, I watched the video titled *"Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler – Kerem Demirtaş & Erdi Daşdemir"*.

This video presents a discussion on how data science relates to industrial engineering. It explains how industrial engineers use data to improve decision-making processes within organizations and optimize efficiency through proper design and analysis.

The discussion also highlights the importance of data analytics skills for industrial engineers. Many modern engineering problems involve analyzing large datasets, building predictive models, and applying statistical techniques.

In conclusion, the video underlines that knowledge of data science is becoming a necessary skill set for industrial engineers who want to work in areas such as operations research, optimization, and digital transformation.

## (b) Questions

### Open-ended Question

Why are data analytics and data-driven decision making becoming increasingly important for industrial engineers?

**Answer:**\
Because modern organizations generate large amounts of data. Industrial engineers use this data to improve operational efficiency, optimize systems, and support strategic decision making.

### Multiple Choice Question

Which of the following best describes the role of data science in industrial engineering?

A)  Designing physical machines\
B)  Analyzing data to improve systems and decision-making\
C)  Managing human resources\
D)  Producing raw materials

**Correct Answer:** B

## Data Analysis with R

```{r}
library(dslabs)
data("polls_us_election_2016")

my_first <- "Ilayda"
my_birth_year <- 2002

k <- (nchar(my_first) + my_birth_year) %% 15 + 8
k
```

```{r}
data <- polls_us_election_2016

if (k %% 2 == 0) {
  head(data, k)
} else {
  tail(data, k)
}
```

```{r}
sum(is.na(data))
```

```{r}
na_per_column <- colSums(is.na(data))
sort(na_per_column, decreasing = TRUE)[1:8]
```

```{r}
new_data <- data

for (col in names(new_data)) {
  if (is.numeric(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k
    
  } else if (inherits(new_data[[col]], "Date")) {
    new_data[[col]][is.na(new_data[[col]])] <- as.Date("2002-01-01")
    
  } else {
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
  }
}
```

```{r}
if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}
```

```{r}
sum(is.na(new_data))
anyNA(new_data)
```
